$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-09-16 paper/paper.tex
Second pass to example

    \draw[->] (send-x) -- node[left] {$x$} (sync);
    \draw[->] (send-y) -- node[right] {$y$} (sync);
    \draw[->] (sync.35) -- node[right] {$z$} (recv-z.240);
    \draw[->] (sync) -- (recv-z);
  \end{tikzpicture}
  \caption{The courier system: two senders $S_1$ and $S_2$, one receiver $R$ and one courier $C$.}
  \label{fig:example-process}
\end{figure}

@@

We continue this example by providing typing derivations for these processes in \autoref{leftover-typing}.
We use graded types for the usage annotations of the communication channels $x$, $y$, and $z$: both processes $\func{send} \; x$ and $\func{send} \; y$ consume $1$ output multiplicity; $\func{recv} \; z$ consumes $2$ input multiplicities.
Dually, the process $\func{carry} \; x \; y \; z$ consumes one input multiplicity on $x$ and $y$, and two output multiplicities on $z$.

[TODO: type of data being transmitted]
\end{example}

>>>>

    \draw[->] (send-x) -- node[left] {$x$} (sync);
    \draw[->] (send-y) -- node[right] {$y$} (sync);
    \draw[->] (sync.35) -- node[right] {$z$} (recv-z.240);
    \draw[->] (sync) -- (recv-z);
  \end{tikzpicture}
  \caption{The courier system: two \textcolor{orange}{senders} $S_1$ and $S_2$, one \textcolor{green}{receiver} $R$ and one \textcolor{blue}{courier} $C$.}
  \label{fig:example-process}
\end{figure}

@@

We continue this example and provide typing derivations for these processes in \autoref{leftover-typing}.
We use \textbf{shared types} for the type of data that is being sent over these channels, and \textbf{linear types} for its usage annotations.
We use \textbf{graded types} for the usage annotations of the communication channels $x$, $y$, and $z$ themselves: both processes $\func{send} \; x$ and $\func{send} \; y$ consume $1$ output multiplicity; $\func{recv} \; z$ consumes $2$ input multiplicities.
Dually, the process $\func{carry} \; x \; y \; z$ consumes one input multiplicity on $x$ and $y$, and two output multiplicities on $z$.
\end{example}
